---
title: "erinea_OriginalHomeworkCode_03"
author: "Erin Anderson"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import csv, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
zombie_data <- read.csv("~/Desktop/zombies.csv", sep = ",", header = TRUE, stringsAsFactors = FALSE)
zombie_data
```

## Problem 1: Means
```{r read csv, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
height <- zombie_data[["height"]]
weight <- zombie_data[["weight"]]
killed <- zombie_data[["zombies_killed"]]
age <- zombie_data[["age"]]
years_of_education <- zombie_data[["years_of_education"]]
mean_height <- mean(height)
mean_height
mean_weight <- mean(weight)
mean_weight
mean_age <- mean(age)
mean_age
mean_killed <- mean(killed)
mean(killed)
mean_years_of_education <- mean(years_of_education)
mean_years_of_education
```

## Problem 1: Standard Deviations
```{r standard deviation, include=TRUE}
sum_squared_diff_age <- sum((age - mean_age)^2)
population_sd_age <- sqrt(sum_squared_diff_age / length(age))
population_sd_age
sum_squared_diff_weight <- sum((weight - mean_weight)^2)
population_sd_weight <- sqrt(sum_squared_diff_weight / length(weight))
population_sd_weight
sum_squared_diff_height <- sum((height - mean_height)^2)
population_sd_height <- sqrt(sum_squared_diff_height / length(height))
population_sd_height
sum_squared_diff_killed <- sum((killed - mean_killed)^2)
population_sd_killed <- sqrt(sum_squared_diff_killed / length(killed))
population_sd_killed
sum_squared_diff_years <- sum((years_of_education - mean_years_of_education)^2)
population_sd_years <- sqrt(sum_squared_diff_years / length(years_of_education))
population_sd_years
```

## Problem 2: Age
```{r boxplot of age, include=TRUE}
library(ggplot2)
box_plot <- ggplot(data = zombie_data, aes(x = gender, y = (age)))
box_plot <- box_plot + geom_boxplot()
box_plot <- box_plot + theme(axis.text.x = element_text(angle = 90))
box_plot <- box_plot + ylab("Age") + xlab("Gender")
box_plot
```

## Problem 2: Weight
```{r boxplot of weight, include=TRUE}
library(ggplot2)
box_plot_2 <- ggplot(data = zombie_data, aes(x = gender, y = (weight)))
box_plot_2 <- box_plot_2 + geom_boxplot()
box_plot_2 <- box_plot_2 + theme(axis.text.x = element_text(angle = 90))
box_plot_2 <- box_plot_2 + ylab("Weight") + xlab("Gender")
box_plot_2
```

## Problem 2: Height
```{r boxplot of height, include=TRUE}
library(ggplot2)
box_plot_3 <- ggplot(data = zombie_data, aes(x = gender, y = (height)))
box_plot_3 <- box_plot_3 + geom_boxplot()
box_plot_3 <- box_plot_3 + theme(axis.text.x = element_text(angle = 90))
box_plot_3 <- box_plot_3 + ylab("Height") + xlab("Gender")
box_plot_3
```

## Problem 2: Zombies Killed
```{r boxplot of kiled, include=TRUE}
library(ggplot2)
box_plot_4 <- ggplot(data = zombie_data, aes(x = gender, y = (killed)))
box_plot_4 <- box_plot_4 + geom_boxplot()
box_plot_4 <- box_plot_4 + theme(axis.text.x = element_text(angle = 90))
box_plot_4 <- box_plot_4 + ylab("Zombies Killed") + xlab("Gender")
box_plot_4
```

## Problem 2: Years of Education
```{r boxplot of years, include=TRUE}
library(ggplot2)
box_plot_5 <- ggplot(data = zombie_data, aes(x = gender, y = (years_of_education)))
box_plot_5 <- box_plot_5 + geom_boxplot()
box_plot_5 <- box_plot_5 + theme(axis.text.x = element_text(angle = 90))
box_plot_5 <- box_plot_5 + ylab("Years of Education") + xlab("Gender")
box_plot_5
```

## Problem 3: Height and Age
```{r scatterplot 1, include=TRUE}
scatterplot <- ggplot(data = zombie_data, aes(x = age, y = height))
scatterplot <- scatterplot + geom_point()
scatterplot <- scatterplot + geom_smooth(method = "lm")
scatterplot
```

## Problem 3: Weight and Age
```{r scatterplot 2, include=TRUE}
scatterplot_2 <- ggplot(data = zombie_data, aes(x = age, y = weight))
scatterplot_2 <- scatterplot_2 + geom_point()
scatterplot_2 <- scatterplot_2 + geom_smooth(method = "lm")
scatterplot_2
```

## Problem 3: Weight and Height
```{r scatterplot 3, include=TRUE}
scatterplot_3 <- ggplot(data = zombie_data, aes(x = age, y = weight))
scatterplot_3 <- scatterplot_3 + geom_point()
scatterplot_3 <- scatterplot_3 + geom_smooth(method = "lm")
scatterplot_3
```

## Problem 4: Age
```{r histogram 1, include=TRUE}
hist_age <- hist(age, main = "Age",
    xlab = "Age", xlim = c(10,30))
hist_age
```
```{r qqplot 1, include=TRUE}
qqnorm(zombie_data$age, main = "Q-Q Plot of Age")
qqline(zombie_data$age, col = "red")

```

## Problem 4: Weight
```{r histogram 2, include=TRUE}
hist_weight <- hist(weight, main = "Weight",
    xlab = "Weight", xlim = c(100,250))
hist_weight
```
```{r qqplot 2, include=TRUE}
qqnorm(zombie_data$weight, main = "Q-Q Plot of Weight")
qqline(zombie_data$weight, col = "red")

```

## Problem 4: Zombies Killed
```{r histogram 3, include=TRUE}
hist_killed <- hist(killed, main = " Zombies Killed",
    xlab = "Zombies Killed", xlim = c(0,12))
hist_killed
```
```{r qqplot 3, include=TRUE}
qqnorm(zombie_data$zombies_killed, main = "Q-Q Plot of Zombies Killed")
qqline(zombie_data$zombies_killed, col = "red")
```
## Problem 4: Years of Education
```{r histogram 4, include=TRUE}
hist_years <- hist(years_of_education, main = "Years of Education",
    xlab = "Years of Education", xlim = c(0,10))
hist_years
```
```{r qqplot 4, include=TRUE}
qqnorm(zombie_data$years_of_education, main = "Q-Q Plot of Years of Education")
qqline(zombie_data$years_of_education, col = "red")

```
## Problem 4: Height
```{r histogram 5, include=TRUE}
hist_height <- hist(height, main = "Height",
    xlab = "Height", xlim = c(50,90))
hist_height
```

```{r ggplot 5, include=TRUE}
qqnorm(zombie_data$height, main = "Q-Q Plot of Years of Height")
qqline(zombie_data$height, col = "red")
```
## Problem 5: Height
```{r sample height, include=TRUE}
sample_height <- sample(height, 30, replace = FALSE)
mean(sample_height)
standard_dev_height <- sd(sample_height)
standard_dev_height
height_sample_stand_error <- standard_dev_height/sqrt(30)
height_sample_stand_error
lower <- mean_height - qnorm(1 - 0.05/2) * height_sample_stand_error
upper <- mean_height + qnorm(1 - 0.05/2) * height_sample_stand_error 
ci_height <- c(lower, upper)
ci_height
```

## Problem 5: Weight
```{r sample weight, include=TRUE}
sample_weight <- sample(weight, 30, replace = FALSE)
mean(sample_weight)
standard_dev_weight <- sd(sample_weight)
standard_dev_weight
weight_sample_stand_error <- standard_dev_weight/sqrt(30)
weight_sample_stand_error
lower_weight <- mean_weight - qnorm(1 - 0.05/2) * weight_sample_stand_error
upper_weight <- mean_weight + qnorm(1 - 0.05/2) * weight_sample_stand_error 
ci_weight <- c(lower_weight, upper_weight)
ci_weight
```

## Problem 5: Age
```{r sample age, include=TRUE}
sample_age <- sample(age, 30, replace = FALSE)
mean(sample_age)
standard_dev_age <- sd(sample_age)
standard_dev_age
age_sample_stand_error <- standard_dev_age/sqrt(30)
age_sample_stand_error
lower_age <- mean_age - qnorm(1 - 0.05/2) * age_sample_stand_error
upper_age <- mean_age + qnorm(1 - 0.05/2) * age_sample_stand_error 
ci_age <- c(lower_age, upper_age)
ci_age
```

## Problem 5: Zombies Killed
```{r sample killed, include=TRUE}
sample_killed <- sample(killed, 30, replace = FALSE)
mean(sample_killed)
standard_dev_killed <- sd(sample_killed)
standard_dev_killed
killed_sample_stand_error <- standard_dev_killed/sqrt(30)
killed_sample_stand_error
lower_killed <- mean_killed - qnorm(1 - 0.05/2) * killed_sample_stand_error
upper_killed <- mean_killed + qnorm(1 - 0.05/2) * killed_sample_stand_error 
ci_killed <- c(lower_killed, upper_killed)
ci_killed
```

## Problem 5: Years of Education
```{r sample education, include=TRUE}
sample_years <- sample(years_of_education, 30, replace = FALSE)
mean(sample_years)
standard_dev_years <- sd(sample_years)
standard_dev_years
years_sample_stand_error <- standard_dev_years/sqrt(30)
years_sample_stand_error
lower_years <- mean_years_of_education - qnorm(1 - 0.05/2) * years_sample_stand_error
upper_years <- mean_years_of_education + qnorm(1 - 0.05/2) * years_sample_stand_error 
ci_years <- c(lower_years, upper_years)
ci_years
```

## Problem 6: Height
```{r 100 random samples - height, include=TRUE}
height_99 <- NULL
for (i in 1:99) {
    height_99[i] <- mean(sample(height, 30, replace = FALSE))
}
all_100 <- height_99 + mean(sample_height)
mean(all_100)
sd(all_100)

#I'm not sure how to best include the past sample
```

## Problem 6: Weight
```{r 100 random samples -weight, include=TRUE}
weight_99 <- NULL
for (i in 1:99) {
    weight_99[i] <- mean(sample(weight, 30, replace = FALSE))
}
all_100_w <- weight_99 + mean(sample_weight)
mean(all_100_w)
sd(all_100_w)
```

## Problem 6: Age
```{r 100 random samples - age, include=TRUE}
age_99 <- NULL
for (i in 1:99) {
    age_99[i] <- mean(sample(age, 30, replace = FALSE))
}
all_100_a <- age_99 + mean(sample_age)
mean(all_100_a)
sd(all_100_a)
```

## Problem 6: Zombies Killed
```{r 100 random samples - killed, include=TRUE}
killed_99 <- NULL
for (i in 1:99) {
    killed_99[i] <- mean(sample(killed, 30, replace = FALSE))
}
all_100_k <- killed_99 + mean(sample_killed)
mean(all_100_k)
sd(all_100_k)
```

## Problem 6: Years of Education
```{r 100 random samples - years, include=TRUE}
years_99 <- NULL
for (i in 1:99) {
    years_99[i] <- mean(sample(years_of_education, 30, replace = FALSE))
}
all_100_y <- years_99 + mean(sample_years)
mean(all_100_y)
sd(all_100_y)
```
